---
title: "Problems Met in Building the Book"
author: "Sen Yang"
date: "9/10/2018"
output:
 pdf_document:
  number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Information About the Current R Session

```{r session, echo=FALSE}
sessionInfo()
```

# Installation and Building Process

- Clone the source of Hadley Wickham's **Advanced R Programming** from his GitHub repository to a local space on my computer
- Follow the instruction at <https://bookdown.org/yihui/bookdown/get-started.html> 

However, in the process of building the book, several probelms are met and solved as followings.

# Problems Met in Building the Book

## Problem 1

Installed all packages needed.

After I clicked `Build All` button on `Build` tab, Error messages would be shown in the `Build` window. Just follow the error messages to install all missing packages and rebuild the book.
If any package is not included on CRAN, install it directly from *github* by `devtools`, like `'devtool::install_github()'`.

## Problem 2

Installed the latest version of [XQuartz](https://www.xquartz.org/) and [Pandoc](https://pandoc.org/installing.html).

## Problem 3

When installing package `TinyTex`, I got a error as

```
destination /usr/local/bin not writable, no links from /Users/hagen/Library/TinyTeX/bin/x86_64-darwin. add of symlinks had 1 error(s), see messages above. add of symlinks had 1 error(s), see messages above. tlmgr: An error has occurred. See above messages. Exiting.

```

Solved it by following the instruction at <https://github.com/yihui/tinytex/issues/24>.

## Problem 4

The font "Inconsolata" cannot be found. 
Just Google it and then install on my computer. Rebuild the book.


